Software Quality Assurance in INDIGO-DataCloud project: a converging evolution of software engineering practices to support European Research e-Infrastructures

### 2020-01-03 paper-jgc.tex
Comment unnecessary references

\bibitem{h2020}
\emph{Horizon 2020} -- European Commission.
[Online]. Available: \url{https://ec.europa.eu/programmes/horizon2020/}.
[Accessed 14 Feb. 2019].

@@

\bibitem{aiftimiei}
C Aiftimiei, A Ceccanti, D Dongiovanni, A Di Meglio and F Giacomini,
``Improving the quality of EMI Releases by leveraging the EMI Testing Infrastructure,''
\emph{J. Phys. Conf. Ser.},
vol. 396, no. 5, 2012.

@@

\bibitem{soltesz}
S. Soltesz \emph{et al.},
``Container-based Operating System Virtualization: A Scalable, High-performance Alternative to Hypervisors,''
\emph{SIGOPS Oper. Syst. Rev.},
vol. 41, no. 3, pp. 275--287, Mar. 2007.

\bibitem{radatz}
``IEEE Standard Glossary of Software Engineering Terminology,''
\emph{IEEE Std. 610.12--1990}, pp.1--84, Dec. 31 1990.

\bibitem{sommerville}
I. Sommerville,
``Integrated requirements engineering: A tutorial,''
\emph{IEEE Softw.}, vol. 22, no. 1, pp. 16--23, Jan.--Feb. 2005.

\bibitem{tashtoush}
Y. Tashtoush, Z. Odat, I. Alsmadi, M. Yatim,
``Impact of programming features on code readability,''
\emph{Int. J. Softw. Eng. Appl.},
vol. 7, no. 6, pp. 441--458, Nov. 2013.

\bibitem{buse}
R. P. Buse and W. R. Weimer,
``Learning a metric for code readability,''
\emph{IEEE Trans. Softw. Eng.},
vol. 36, no. 4, pp. 546--558, Jul. 2010.

\bibitem{baggen}
R. Baggen, J. P. Correia, K. Schill and J. Visser,
``Standardized code quality benchmarking for improving software maintainability,''
\emph{Softw. Qual. J.},
vol. 20, no. 2, pp. 287--307, Jun. 2012.

\bibitem{fenton}
N. Fenton  and  S.  L.  Pfleeger,
``Software  Metrics:  A  Rigorous  and  Practical Approach,''
\emph{International Thomson Computer Press},
London, UK, second edition, 1997.

\bibitem{capers}
J. Capers,
``Applied Software Measurement (2nd Ed.): Assuring Productivity and Quality,''
\emph{McGraw Hill}, New York, NY, USA, 1997.

\bibitem{goodman}
P. Goodman,
``Practical Implementation of Software Metrics,''
\emph{McGraw Hill}, New York, NY, USA, 1993.

\bibitem{mccabe}
T. J. McCabe,
``A Complexity Measure,''
\emph{IEEE Trans. Softw. Eng.},
vol. 2, no. 4, pp. 308--320, Dec. 1976.

\bibitem{chidamber}
S. R. Chidamber and C. E. Kemerer,
``A metrics suite for Object--oriented design,''
\emph{IEEE Trans. Softw. Eng.},
vol. 20, no. 6, pp. 476--493, Jun 1994.

\bibitem{lorenz}
M. Lorenz and J. Kidd,
\emph{Object--Oriented Software Metrics: A Practical Approach}.
Prentice-Hall, Inc., Upper Saddle River, NJ, USA, 1994.

\bibitem{myers}
G. J. Myers, C. Sandler and T. Badgett,
\emph{The art of software testing, 3rd Ed.}.
Wiley Publishing, Dec. 2011.

\bibitem{athanasiou}
D. Athanasiou, A. Nugroho, J. Visser and A. Zaidman,
``Test Code Quality and Its Relation to Issue Handling Performance,''
\emph{IEEE Trans. Softw. Eng.},
vol. 40, no. 11, pp. 1100--1125, Nov. 2014.

\bibitem{horgan}
J. R. Horgan, S. London and M. R. Lyu,
``Achieving software quality with testing coverage measuring,''
\emph{Comput.},
vol. 27, no. 9, pp. 60--69, Sep. 1994.

>>>>

%\bibitem{h2020}
%\emph{Horizon 2020} -- European Commission.
%[Online]. Available: \url{https://ec.europa.eu/programmes/horizon2020/}.
%[Accessed 14 Feb. 2019].

@@

%\bibitem{aiftimiei}
%C Aiftimiei, A Ceccanti, D Dongiovanni, A Di Meglio and F Giacomini,
%``Improving the quality of EMI Releases by leveraging the EMI Testing Infrastructure,''
%\emph{J. Phys. Conf. Ser.},
%vol. 396, no. 5, 2012.

@@

%\bibitem{soltesz}
%S. Soltesz \emph{et al.},
%``Container-based Operating System Virtualization: A Scalable, High-performance Alternative to Hypervisors,''
%\emph{SIGOPS Oper. Syst. Rev.},
%vol. 41, no. 3, pp. 275--287, Mar. 2007.

%\bibitem{radatz}
%``IEEE Standard Glossary of Software Engineering Terminology,''
%\emph{IEEE Std. 610.12--1990}, pp.1--84, Dec. 31 1990.

%\bibitem{sommerville}
%I. Sommerville,
%``Integrated requirements engineering: A tutorial,''
%\emph{IEEE Softw.}, vol. 22, no. 1, pp. 16--23, Jan.--Feb. 2005.

%\bibitem{tashtoush}
%Y. Tashtoush, Z. Odat, I. Alsmadi, M. Yatim,
%``Impact of programming features on code readability,''
%\emph{Int. J. Softw. Eng. Appl.},
%vol. 7, no. 6, pp. 441--458, Nov. 2013.

%\bibitem{buse}
%R. P. Buse and W. R. Weimer,
%``Learning a metric for code readability,''
%\emph{IEEE Trans. Softw. Eng.},
%vol. 36, no. 4, pp. 546--558, Jul. 2010.

%\bibitem{baggen}
%R. Baggen, J. P. Correia, K. Schill and J. Visser,
%``Standardized code quality benchmarking for improving software maintainability,''
%\emph{Softw. Qual. J.},
%vol. 20, no. 2, pp. 287--307, Jun. 2012.

%\bibitem{fenton}
%N. Fenton  and  S.  L.  Pfleeger,
%``Software  Metrics:  A  Rigorous  and  Practical Approach,''
%\emph{International Thomson Computer Press},
%London, UK, second edition, 1997.

%\bibitem{capers}
%J. Capers,
%``Applied Software Measurement (2nd Ed.): Assuring Productivity and Quality,''
%\emph{McGraw Hill}, New York, NY, USA, 1997.

%\bibitem{goodman}
%P. Goodman,
%``Practical Implementation of Software Metrics,''
%\emph{McGraw Hill}, New York, NY, USA, 1993.

%\bibitem{mccabe}
%T. J. McCabe,
%``A Complexity Measure,''
%\emph{IEEE Trans. Softw. Eng.},
%vol. 2, no. 4, pp. 308--320, Dec. 1976.

%\bibitem{chidamber}
%S. R. Chidamber and C. E. Kemerer,
%``A metrics suite for Object--oriented design,''
%\emph{IEEE Trans. Softw. Eng.},
%vol. 20, no. 6, pp. 476--493, Jun 1994.

%\bibitem{lorenz}
%M. Lorenz and J. Kidd,
%\emph{Object--Oriented Software Metrics: A Practical Approach}.
%Prentice-Hall, Inc., Upper Saddle River, NJ, USA, 1994.

%\bibitem{myers}
%G. J. Myers, C. Sandler and T. Badgett,
%\emph{The art of software testing, 3rd Ed.}.
%Wiley Publishing, Dec. 2011.

%\bibitem{athanasiou}
%D. Athanasiou, A. Nugroho, J. Visser and A. Zaidman,
%``Test Code Quality and Its Relation to Issue Handling Performance,''
%\emph{IEEE Trans. Softw. Eng.},
%vol. 40, no. 11, pp. 1100--1125, Nov. 2014.

%\bibitem{horgan}
%J. R. Horgan, S. London and M. R. Lyu,
%``Achieving software quality with testing coverage measuring,''
%\emph{Comput.},
%vol. 27, no. 9, pp. 60--69, Sep. 1994.
